---
title: "Marriage Licence Statistics"
author: "Sakura Noskor "
thanks: "Code and data are available at: https://github.com/NotSakura/Week2_304.git"
date: today
date-format: long
abstract: "Mariage Licencein Toronto and how they fluctuate."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)

data <- read_csv(here::here("data/raw_data/cleaned_data.csv"))
```


# Introduction

You can and should cross-reference sections and sub-sections. We use @citeR and @rohan and @opendata.

The remainder of this paper is structured as follows. @sec-data....



# Data {#sec-data}

Some of our data is of penguins (@fig-mar).

```{r}
#| label: fig-mar
#| fig-cap: Number of mariage licence in toronto
#| echo: false

data |> ggplot(aes(x = date, y = marriage_licenses)) + geom_point()
```

Talk more about it.

And also planes . (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)


Talk way more about it. 



# Results





# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this. 

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage



# References


